Benefits and risks of diversification for individual fishers

### 2017-02-09 portfolio/text/anderson-etal-rev-pfx.tex
Draft a significance statement

% Please add here a significance statement to explain the relevance of your work
\significancestatement{TODO}

@@

% 250:
\begin{abstract}
Individuals relying on the extraction of natural resources for their
livelihood---fishers, farmers, miners, and loggers, among others---face high
levels of income variability driven by a mix of environmental, biological,
management, and
economic factors. Key to managing these industries is identifying
how regulatory actions and individual behaviour affect income variability and, by
extension, economic stability and the sustainable use of natural resources. In
commercial fisheries, communities and vessels fishing a greater diversity of
species have less revenue variability than those fishing fewer species.
However, it is unclear if these benefits extend to the actions of individual
fishers and how year-to-year changes in diversification affect revenue and
revenue variability. Here, we evaluate two axes by which fishers in Alaska
can diversify fishing
activities. We show that, despite increasing specialization over the last 30
years, fishing a set of permits with higher species diversity reduces individual revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of existing permits has a fishery-dependent effect on revenue and is
usually (87\% probability) associated with increased revenue uncertainty
the following year. Our results demonstrate that the most effective option for
individuals to decrease revenue variability is to
participate in additional or more diverse fisheries. However, this option is
expensive, often limited by regulations such as license limitation or catch share programs, and
consequently unavailable to many individuals. With increasing climatic variability,
it will be particularly important that
individuals relying on natural resources for their livelihood have effective
strategies to reduce income variability.
 % (`r g2_dens`% probability)
\end{abstract}

@@

\acknow{This work was conducted as part of the National Center for Ecological
  Analysis and Synthesis working group ``Applying portfolio effects to the Gulf
  of Alaska ecosystem: Did multi-scale diversity buffer against the Exxon
  Valdez oil spill?''. We thank other participants of the
  working group for helpful discussions. Additional support was provided by a
  David H. Smith Conservation Research Fellowship (S.C.A.) and the NOAA Fisheries'
  Spatial Economics Toolbox for Fisheries (FishSET) Project (J.T.W).}

>>>>

% Please add here a significance statement to explain the relevance of your work
% <120 words
\significancestatement{
Individuals relying on natural resources to sustain their livelihoods,
such as fishers, farmers, and forestry workers,
face high levels of income variability.
For fishers, targeting a diversity of species has been shown to
reduce community- and vessel-level revenue variability
but the individual-level consequences are unknown.
Our work demonstrates that individuals in fisheries targeting
a diversity of species
and individuals that participate in multiple fisheries
buffer income variability compared to less diverse individuals.
However, adjusting (increasing or decreasing) species diversity from year-to-year
usually increases individual-level revenue variability.
\textbf{OR}
However, specializing from year-to-year
(reducing species diversity)
tends to be associated with increased revenue
as well as increased revenue variability
when controlling for effort.
The most effective option for individuals to
reduce revenue variability via diversification
--- purchasing additional permits ---
is also expensive, often limited by regulations,
and therefore unavailable to many.
}
% We ask how multiple forms of
% species diversification affect individual-level
% revenue and revenue variability for Alaskan fishers.

@@

% 250:
\begin{abstract}
Individuals relying on the extraction of natural resources for their
livelihood face high
levels of income variability driven by a mix of environmental, biological,
management, and
economic factors. Key to managing these industries is identifying
how regulatory actions and individual behaviour affect income variability and, by
extension, economic stability and the sustainable use of natural resources. In
commercial fisheries, communities and vessels fishing a greater diversity of
species have less revenue variability than those fishing fewer species.
However, it is unclear if these benefits extend to the actions of individual
fishers and how year-to-year changes in diversification affect revenue and
revenue variability. Here, we evaluate two axes by which fishers in Alaska
can diversify fishing
activities. We show that, despite increasing specialization over the last 30
years, fishing a set of permits with higher species diversity reduces individual revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of existing permits has a fishery-dependent effect on revenue and is
usually (87\% probability) associated with increased revenue uncertainty
the following year. Our results demonstrate that the most effective option for
individuals to decrease revenue variability is to
participate in additional or more diverse fisheries. However, this option is
expensive, often limited by regulations such as license limitation or catch share programs, and
consequently unavailable to many individuals. With increasing climatic variability,
it will be particularly important that
individuals relying on natural resources for their livelihood have effective
strategies to reduce income variability.
 % (`r g2_dens`% probability)
\end{abstract}

@@

\acknow{This work was conducted as part of the National Center for Ecological
  Analysis and Synthesis working group ``Applying portfolio effects to the Gulf
  of Alaska ecosystem: Did multi-scale diversity buffer against the \textit{Exxon
  Valdez} oil spill?''. We thank other participants of the
  working group for helpful discussions. Additional support was provided by a
  David H. Smith Conservation Research Fellowship (S.C.A.) and the NOAA Fisheries'
  Spatial Economics Toolbox for Fisheries (FishSET) Project (J.T.W).}
